\texttt{ensmallen}: a flexible C++ library for efficient function optimization

### 2018-10-17 doc/mlsys_paper/paper.tex
crop and shrink figure with learning curves

This pluggability makes it easy to use {\tt ensmallen} to generate comparisons
between optimizers, and in Figure \ref{fig:learning_curve} we use these six
lines of code to generate learning curves for each of these six optimizers on
the {\tt YearPredictionMSD} dataset from the UCI dataset
repository~\cite{ucimlrepository}. % TODO: add to bibtex
In addition, any other optimizers for separable differentiable objective
functions could be dropped into place.

\begin{figure}[h!]
\centering
\includegraphics[width=\textwidth]{experiments/learning_curves.png}
\label{fig:learning_curve}
\caption{Learning curves for six {\tt ensmallen} optimizers on {\tt
YearPredictionMSD} dataset over 5 epochs of training.  Optimizers can be
tuned for better performance.}
\end{figure}

>>>>

This pluggability makes it easy to use {\tt ensmallen} to generate comparisons
between optimizers. In Fig.~\ref{fig:learning_curve} we use these six
lines of code to generate learning curves for each of these six optimizers on
the {\tt YearPredictionMSD} dataset from the UCI dataset
repository~\cite{ucimlrepository}. % TODO: add to bibtex
In addition, any other optimizers for separable differentiable objective
functions can be dropped into place.

\begin{figure}[h!]
\begin{minipage}[t]{1\textwidth}
\begin{minipage}{0.60\textwidth}
  \centering
  \includegraphics[width=\textwidth,height=0.45\textwidth]{experiments/learning_curves_crop.png}
\end{minipage}
\hfill
\begin{minipage}{0.38\textwidth}
  \centering
  \caption
    {
    Learning curves for six {\tt ensmallen} optimizers 
    for optimizing a linear regression function 
    on the {\tt YearPredictionMSD} dataset~\cite{ucimlrepository}
    over 5 epochs of training.
    Optimizers can be tuned for better performance.
    }
  \label{fig:learning_curve}
\end{minipage}
\end{minipage}
\end{figure}
